Appendix

### 2020-03-16 manuscript/appendix.Rmd
create nonlinear clay vs tn plot

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  geom_line(data = fit_tn_pred, aes(x = exp(ag), y = exp(tn_pred)), 
             color = "red") +
  annotate("text", x = 14, y = 12000, label = get_formula("log(tn)", fit_tn), 
           size = 2) +
  ylab("log(TN) (ug/L)") +
  xlab("log(Percent Agriculture)") +
  scale_x_log10() + scale_y_log10() +
  theme_cowplot(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
    geom_line(data = fit_tp_pred, aes(x = exp(ag), y = exp(tp_pred)), 
             color = "red") +
  annotate("text", x = 14, y = 900, label = get_formula("log(tp)", fit_tp), 
           size = 2) +
  ylab("log(TP) (ug/L)") +
  xlab("log(Percent Agriculture)") +
  scale_x_log10() + scale_y_log10() +
  theme_cowplot()
)

@@

>>>>

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  geom_line(data = fit_tn_pred, aes(x = exp(ag), y = exp(tn_pred)), 
             color = "red") +
  annotate("text", x = 14, y = 12000, label = get_formula("log(tn)", fit_tn), 
           size = 2) +
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture") +
  scale_x_log10() + scale_y_log10() +
  theme_cowplot(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
    geom_line(data = fit_tp_pred, aes(x = exp(ag), y = exp(tp_pred)), 
             color = "red") +
  annotate("text", x = 14, y = 900, label = get_formula("log(tp)", fit_tp), 
           size = 2) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture") +
  scale_x_log10() + scale_y_log10() +
  theme_cowplot()
)

@@

```{r clay-nonlinear, fig.cap = "Scatterplot showing the non-linear relationship between watersehd clay content and lake TN concentration. Vertical dashed line shows transition between a positive and a negative correlation (r) between the two variables. Solid red line shows the fit of a generalized additive model from the mgcv R package.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
# Why was the clay coefficient negative in the TN model?
# re_brms <- readRDS("data/mcmc/re_brms.rds")
# re_brms[[8]]$formula
dt       <- # readRDS("data/dt.rds") %>%
  readRDS("../data/dt_scaled.rds") %>%
  dplyr::select(clay_pct, hu12_ppt_mean, hu12_baseflow_mean, 
                buffer_cultivated_crops, iwsla_ratio, soil_org_carbon,
                wetlands,
                maxdepth, ag, tn, lagoslakeid)

test <- readRDS("../data/dt_scaled.rds") %>%
  dplyr::select(lagoslakeid, clay_pct, tn) %>%
  left_join(
    dplyr::select(readRDS("../data/dt.rds"), lagoslakeid, clay_pct, tn), 
    by = "lagoslakeid") %>%
  setNames(c("lagoslakeid", "clay_pct_scaled", "tn_scaled", 
  "clay_pct_raw", "tn_raw")) %>%
  mutate_all(as.numeric)
labs_key              <- data.frame(clay_pct_raw = seq(0, 30, length.out = 5))
fit <- lm(clay_pct_scaled ~ clay_pct_raw, data = test)
labs_key$clay_pct_scaled <- round(predict(fit, newdata = labs_key), 1)

# https://stats.stackexchange.com/a/35922/49019
library(mgcViz)
b <- bamV(tn ~ s(clay_pct, k = 4), data = dt)
o <- plot(sm(b, 1), nsim = 50) # 50 posterior simulations 
o + l_fitLine(colour = "red") + l_points(size = 0.8, shape = 19) +
  geom_vline(xintercept = 0.765, linetype = "dashed") +
  scale_x_continuous(breaks = labs_key$clay_pct_scaled, 
                     labels = labs_key$clay_pct_raw, 
                     limits = c(-2, 3)) +
  xlab("Clay content (%)") + ylab("log(TN (ug/L))") +
  annotate("text", x = -1, y = 3.3, label = paste0("r = ", 
           round(broom::tidy({
             dplyr::filter(dt, clay_pct < 0.765) %$% cor.test(clay_pct, tn)
           })$estimate, 3))) +
  annotate("text", x = 2, y = 3.3, label = paste0("r = ", 
        round(broom::tidy({
          dplyr::filter(dt, clay_pct > 0.765) %$% cor.test(clay_pct, tn)
          })$estimate, 3)))
```
